Price floors and employer preferences: Evidence from a minimum wage experiment

### 2025-04-03 posts/Horton/Horton2024.qmd
added Horton2025_slides.html AboutEditor.html

---
title: "Investing in infants: the lasting effects of cash transfers to new families"
subtitle: "By Andrew Barr, Jonathan Eggleston, Alexander A. Smith"
author: "Seiro Ito"
format:
  revealjs: 
    slide-number: true
    chalkboard: 
      buttons: false
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/BarrEgglestonSmith/BarrEgglestonSmith2022.html>
    theme: sky
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
#width: 1000
bibliography: ../seiro.bib
# If it is 2 levels up, ../../seiro.bib
resources:
  - BarrEgglestonSmith2022.pdf
# quarto render BarrEgglestonSmith2022.qmd
---
<style>
:root{--r-main-font-size: 36px;}
.reveal h1, .reveal h2, .reveal h3, .reveal h4, .reveal h5 {
              text-transform: none;
      }
.spacer {
    margin-top: 20px;
}
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>

## ECD Long-run effects

>>>>

---
title: "Price floors and employer preferences: Evidence from a minimum wage experiment"
subtitle: "By John J. Horton"
author: "Seiro Ito"
format:
  revealjs: 
    slide-number: true
    chalkboard: 
      buttons: false
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/Horton/Horton2025.html>
    theme: sky
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
#width: 1000
bibliography: ../seiro.bib
# If it is 2 levels up, ../../seiro.bib
resources:
  - Horton2025.pdf
# quarto render Horton2025.qmd
---
<style>
:root{--r-main-font-size: 36px;}
.reveal h1, .reveal h2, .reveal h3, .reveal h4, .reveal h5 {
              text-transform: none;
      }
.spacer {
    margin-top: 20px;
}
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>

## Firms' minimum wage adjustments

MW&uarr;...,,,

* Employment head counts&darr;
* Employment hours&darr;
* Nonmonetary compensation&darr;
* Profits&darr;
* Output prices&uarr;
* Labour productivity &uarr; (labour-labour substitution)

## This paper

* Online job platform: Post and bid
* Random assignment of hourly MW: $2, $3, $4
* Applicants: Not aware of MW, but bid < MW not accepted
* Employers: Not aware of MW, see applicant profiles
* Headcounts&darr; little
* Hours&darr by 27% for low wage jobs
* Employment substitution towards more productive workers

### 2025-04-03 posts/Horton/Horton2024_slides.qmd
added Horton2025_slides.html AboutEditor.html

---
title: "Price floors and employer preferences: Evidence from a minimum wage experiment"
subtitle: "By John J. Horton"
author: "Seiro Ito"
format:
  revealjs: 
    slide-number: true
    chalkboard: 
      buttons: false
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/Horton/Horton2025.html>
    theme: sky
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
#width: 1000
bibliography: ../seiro.bib
# If it is 2 levels up, ../../seiro.bib
resources:
  - Horton2025.pdf
# quarto render Horton2025.qmd
---
<style>
:root{--r-main-font-size: 36px;}
.reveal h1, .reveal h2, .reveal h3, .reveal h4, .reveal h5 {
              text-transform: none;
      }
.spacer {
    margin-top: 20px;
}
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>

>>>>

---
title: "Price floors and employer preferences: Evidence from a minimum wage experiment"
subtitle: "By John J. Horton"
author: "Seiro Ito"
format:
  revealjs: 
    slide-number: true
    chalkboard: 
      buttons: false
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/Horton/Horton2025_slides.html>
    theme: sky
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
#width: 1000
bibliography: ../seiro.bib
# If it is 2 levels up, ../../seiro.bib
resources:
  - Horton2025_slides.pdf
# quarto render Horton2025_slides.qmd
---
<style>
:root{--r-main-font-size: 36px;}
.reveal h1, .reveal h2, .reveal h3, .reveal h4, .reveal h5 {
              text-transform: none;
      }
.spacer {
    margin-top: 20px;
}
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>
